sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-23 doc/paper.Rmd
Add examples to paper

```{r, eval=FALSE, echo=TRUE}
fit_spatiotemporal <- sdmTMB(
  density ~ s(depth), family = tweedie(link = "log"), data = pcod, mesh = mesh
  time = "year", spatial = "off", spatiotemporal = "ar1"
)
```

@@

## Speed comparison

>>>>

```{r, eval=FALSE, echo=TRUE}
fit_spatiotemporal <- sdmTMB(
  density ~ s(depth), family = tweedie(link = "log"), data = pcod, mesh = mesh,
  time = "year", spatial = "off", spatiotemporal = "ar1"
)
```

We could generate a standardized index from that fit with:

```{r, eval=FALSE, echo=TRUE}
p <- predict(fit_spatiotemporal, newdata = qcs_grid, return_tmb_object = TRUE)
ind <- get_index(p)
```

As a third example, we could model presence/absence of Pacific cod (`present`) with a time-varying quadratic effect of depth, an independent mean each year, a spatial random field, and IID spatiotemporal fields:

```{r, eval=TRUE, echo=FALSE}
# restore 'present' column
pcod <- sdmTMB::pcod
```

```{r, eval=FALSE, echo=TRUE}
fit_spatiotemporal_tv <- sdmTMB(
  present ~ 0 + as.factor(year), 
  time_varying = ~ 0 + poly(depth, 2), 
  family = binomial(), data = pcod, mesh = mesh,
  time = "year", spatial = "on", spatiotemporal = "iid"
)
```

@@

# Speed comparison
